Dynamics of Colombo's Top: Generating Exoplanet Obliquities from Planet-Disk Interactions

### 2020-08-17 writeups/Su_disk_disp.tex
small typos

\textcolor{Corr}{In practice, planets are not expected to form in isolation.
\citet{millholland_disk} point out that one effect of a companion planet is that
$g$ and $\eta$ for the planet of interest never decay below the Laplace-Lagrange
secular nodal precession frequency. This does not affect the methodology of our
analysis, but has some small effects on our detailed results: (i) the
adiabaticity criterion must be modified slightly as $\rdil{\ln \eta}{t}$ is no
longer constant but asymptotes to zero as $\eta$ decreases, (ii) the planet may
never undergo separatrix crossing if their $\eta_{\star}$ (which depends on
$\theta_{\rm sd, i}$) in the absence of the companions is too small, and (iii)
the planetary obliquities will oscillate even when the disk has fully evaporated
(as $\uv{l}$ is no longer constant). An interesting consequence of (ii) is that
an outer planet may experience separatrix crossing before an inner planet does.
The dynamics can be even more complex if the two planets are in mean motion
resonance \citep[e.g.][]{millholland2019obliquity}.}

>>>>

\textcolor{Corr}{In practice, planets are not expected to form in isolation.
\citet{millholland_disk} point out that one effect of a companion planet is that
$g$ for the planet of interest never decays below the Laplace-Lagrange
secular nodal precession frequency. Therefore, $\eta$ has a minimum value at
late times. This does not affect the methodology of our analysis, but has some
small effects on our detailed results: (i) the adiabaticity criterion must be
modified slightly as $\rdil{\ln \eta}{t}$ is no longer constant but asymptotes
to zero as $\eta$ decreases, (ii) the planet may never undergo separatrix
crossing if their $\eta_{\star}$ (which depends on $\theta_{\rm sd, i}$) in the
absence of the companions is too small, and (iii) the planetary obliquities will
oscillate even when the disk has fully evaporated (as $\uv{l}$ is no longer
constant). An interesting consequence of (ii) is that an outer planet may
experience separatrix crossing before an inner planet does. The dynamics can be
even more complex if the two planets are in mean motion resonance
\citep[e.g.][]{millholland2019obliquity}.}
